---
title: "index"
format: html
params:
  update_data: true
  results_fn: "CPO Member Survey (Responses)"
  fn: cpo-survey-2025.csv
---

## About

This page downloads, tidies, and visualizes data from a membership survey conducted by the Central Pennsylvania Observers (CPO) astronomy club in late 2024-2025.

## Survey

Direct link: <https://forms.gle/kpwGFo2qpsKmNLya9>

Here is the survey:

<iframe src="https://docs.google.com/forms/d/e/1FAIpQLScWSF5_mUWJHatvsmPOE4APbl48tZv0FjzbnmHj8mmAiWLdPQ/viewform?embedded=true" width="640" height="2286" frameborder="0" marginheight="0" marginwidth="0">Loading…</iframe>

## Preparation

First, we load the external packages (groups of R commands) that we will be using.

```{r}
library("ggplot2")
library("dplyr")
library("googledrive")
```

## Gathering

This section downloads the data from a Google Sheet.

```{r, eval=params$update_data}
#| label: gather-data-from-google
#| message: false
#| echo: true
if (!dir.exists('csv')) {
  message("Creating missing `csv/`.")
  dir.create("csv")
}

if (params$update_data) {
  options(gargle_oauth_email = Sys.getenv("GMAIL_SURVEY"))
  googledrive::drive_auth()

  assertthat::is.string(params$results_fn)
  assertthat::is.string(params$fn)
  assertthat::is.writeable(file.path("csv", params$fn))
  googledrive::drive_download(
    params$results_fn,
    path = file.path("csv", params$fn),
    type = "csv",
    overwrite = TRUE
  )
  message("Data updated.")
} else {
  message("Using stored data.")
}
```

## Cleaning

Next we load the saved data file and then proceed to clean it.

```{r, eval=params$update_data}
#| label: load-saved-data
#| message: false
#| echo: true
cpo <-
  readr::read_csv(file.path("csv", params$fn), show_col_types = FALSE)
```

As of `{r} Sys.time()`, there are `{r} dim(cpo)[1]` responses.

### Rename variables

These are the raw column/variable names.

```{r}
# Google Forms puts the full question in the top row of the data file.
# We use the names() function to extract and print the original questions.
cpo_qs <- names(cpo)
cpo_qs
```

We'll create shorter names to make visualizations.

```{r, eval=params$update_data}
#| label: clean-variable-names-1
cpo_clean <- cpo |>
  dplyr::rename(
    timestamp = "Timestamp",
    activities_2024 = "Which of the following astronomy activities did you participate in during 2024?",
    activities_2025 = "Which of the following astronomy activities do you plan to participate in during 2025?" ,
    activities_volunteer = "Which of the following activities would you like to get more involved with as a volunteer?",
    your_goals = "Do you have any particular astronomy goals?",
    interest_visual = "Rate your level of interest in the following activities. [Visual astronomy]",
    interest_astrophoto = "Rate your level of interest in the following activities. [Astrophotography]",
    interest_sci_talks = "Rate your level of interest in the following activities. [Science-oriented talks]",
    interest_social = "Rate your level of interest in the following activities. [Social gatherings]",
    interest_tutorials = "Rate your level of interest in the following activities. [Tutorials/how-to's]",
    interest_field_trips = "Rate your level of interest in the following activities. [Field trips]",
    interest_gear = "Rate your level of interest in the following activities. [Gear and tech]",
    interest_public_events = "Rate your level of interest in the following activities. [Events for the public]",
    doing_well = "What is something the club does really well?",
    could_improve = "What is something the club could do to improve?",
    not_doing = "Is there something the club should offer that we are not currently doing?",
    comments = "Anything else?",
    name = "Your name (totally optional)"
  )
```

Then, let's create a data dictionary so we don't lose the link between the long and the short names.

```{r}
cpo_dd <- tibble::tibble(questions = cpo_qs, short_names = names(cpo_clean))
```

Next, we gather the `interest_*` variables into a single variable.
